Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-11-26 paper/paper.tex
James's comments

We perform our experiments on systems with dual Intel Xeon E5-2697A v4 processors and 512GBytes RAM,
running Ubuntu 17.04, with GCC 6.3.0 as the compiler. Each machine has a total of thirty two cores.
We run all our experiments with a one thousand second timeout for each instance. All of our
sequential runtimes are from optimised implementations by their original authors which were not
designed with parallelism in mind---that is, speedups from parallelism are genuine improvements over
the state of the art.

@@

With one exception, each plot gives the same conclusion: if we are working with a solving time of at
least $10^2$ milliseconds, then for any problem family and any sequential algorithm, if given the
option of switching to the corresponding parallel algorithm, then we should do so. For the McSplit
algorithm on both labelled, connected instances, the parallel algorithm does not quite catch up to
the sequential algorithm.

@@

We plot aggregate speedups as a function of time in \cref{figure:cliqueas}. For a sequential timeout
of one thousand seconds, we get speedups of thirty to forty in the unlabelled, vertex labelled, and
both labelled, directed cases. In the unlabelled cases, our aggregate speedup are over thirty two,
which is superlinear.  With some detailed knowledge of the underlying sequential algorithm, this
should perhaps not surprise us: for instances with a large solution, once we have found that
solution, a proof of optimality is relatively easy. However, finding that solution can be unusually
hard, particularly since the branching strategy for the connected constraint necessarily interferes
with the tailored search order used by modern clique algorithms.  In contrast, for the both labelled
connected case, our aggregate speedup is barely larger than one. A closer inspection of the results
shows that the search tree is unusually narrow and deep for these instances, making work balance
harder and contention higher.

@@

The third and fourth plots in \Cref{figure:kdownscatters} show that as with the clique algorithm,
this parallelism is reproducible, and that runtimes do not get worse when the number of threads is
increased. (Although not shown, we also tried to parallelise $k{\downarrow}$ using randomised
work-stealing from Intel Cilk Plus---similar to the clique algorithm
\cite{DBLP:journals/topc/McCreeshP15}, doing so gives generally reasonable results on average, but
now repeat runtimes can differ by more than an order of magnitude.)

>>>>

We perform our experiments on systems with dual Intel Xeon E5-2697A v4 processors and 512GBytes RAM,
running Ubuntu 17.04, with GCC 6.3.0 as the compiler. Each machine has a total of thirty-two cores.
We run all our experiments with a one thousand second timeout for each instance. All of our
sequential runtimes are from optimised implementations by their original authors which were not
designed with parallelism in mind---that is, speedups from parallelism are genuine improvements over
the state of the art.

@@

With one exception, each plot gives the same conclusion: if we are working with a solving time of at
least $100$ milliseconds, then for any problem family and any sequential algorithm, if given the
option of switching to the corresponding parallel algorithm, then we should do so. For the McSplit
algorithm on both labelled, connected instances, the parallel algorithm does not quite catch up to
the sequential algorithm.

@@

We plot aggregate speedups as a function of time in \cref{figure:cliqueas}. For a sequential timeout
of one thousand seconds, we get speedups of thirty to forty in the unlabelled, vertex labelled, and
both labelled, directed cases. In the unlabelled cases, our aggregate speedup are over thirty-two,
which is superlinear.  With some detailed knowledge of the underlying sequential algorithm, this
should perhaps not surprise us: for instances with a large solution, once we have found that
solution, a proof of optimality is relatively easy. However, finding that solution can be unusually
hard, particularly since the branching strategy for the connected constraint necessarily interferes
with the tailored search order used by modern clique algorithms.  In contrast, for the both labelled
connected case, our aggregate speedup is barely larger than one. A closer inspection of the results
shows that the search tree is unusually narrow and deep for these instances, making work balance
harder and contention higher.

@@

The third and fourth plots in \Cref{figure:kdownscatters} show that as with the clique algorithm,
this parallelism is reproducible, and that runtimes do not get worse when the number of threads is
increased. (Although not shown, we also tried to parallelise $k{\downarrow}$ using randomised
work-stealing from Intel Cilk Plus. Doing so gives generally reasonable results on average, as it
does for the clique algorithm \cite{DBLP:journals/topc/McCreeshP15}, but now repeat runtimes can
differ by more than an order of magnitude.)
